Sampling Frequency in the Dynamic Speckle Analysis

### 2019-09-02 article/article_1.tex
artigo coregido

\title{Importance of Sampling Frequency in the Dynamic Speckle Analysis}
%\tnotetext[mytitlenote]{Fully documented templates are available in the 
%elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

% Group authors per affiliation:
\author{------ ----- -----}
\author{------ ----- -----}

\address{University Federal of Lavras, Lavras, Brazil}
\fntext[myfootnote2]{201518201@posgrad.ufla.br}
\fntext[myfootnote1]{robertobraga@deg.ufla.br }
%

\begin{abstract}
In this article, we show as the variation of sampling frequency, 
in a dynamic speckle analysis, affect the value of some dynamic speckle index, 
in this case: the absolute value of the differences index, the temporal 
speckle standard deviation index and the temporal 
speckle mean index.
we show that  the dynamic speckle index value decrease your maximum excursion with 
the grow of sampling frequency because this affect directly the time integration 
(exposition time) of camera.
\end{abstract}

\begin{keyword}
Frequency sampling \sep
Dynamic speckle index \sep 
Dynamic speckle index \sep 
Dynamic speckle analysis
\end{keyword}

@@

%1) Anuncie o tema e o problema do artigo (forma de pergunta + definiçoes)

The dynamic speckle analysis over biological samples has become  currently  an important
study topic\cite{catalano2019viability,rivera2019sound,gonzalez2018diode,Silva2018,braga2017dynamic} 
to determine the level of biological activity. 
The importance of technical aspects of dynamic speckle analysis,
as the stability of laser illumination level, was analized \cite{gonzalez2018diode}; 
and was showed as indexes as
the absolute values of the differences \cite{cardoso2014,rivera2017selection} are affected in your values
by the variation of illumination level. Thus, It is necessary analyze the effect
of technical parameters that affect the perceived illumination level; In these sense
analyze the effect of sampling frequency in a dynamic speckle analysis

%2) Exponha qual será o percurso (defina seçoes)
%3) Resgate a problematica( Importancia do problema de pesquisa - extenda primer passo)
%4) Relevancia do artigo(importancia para outros del artigo publicado)
%5) Anuncie a hipotesi
%6) Anuncie os objetivos (receita pra demostrar a h.)

@@

\subsection{Exposure time of the camera}
\label{subsec:expositiontime}
The acquisition time,  frame per seconds ($fps$) or sampling frequency ($F_s$), 
in the camera Marlin F-033 will be calculated in the 
 Table \ref{table:1}, where we can see, the shutter register value ($Shutter$), 
time base register value ($Base$),
exposure time ($Exposure$),
exposure time offset ($Offset$) and
effective exposure time ($E$); so that 
\begin{equation}
Exposure= Shutter \times Base,
\end{equation}
\begin{equation}
\frac{1}{F_s}=E= Exposure + Offset.
\end{equation}
Where,  $F_s$ is calculated in relation to the  $E$; being that,
the $Exposure$ represent the photography integration time and $E$ the effective time
between photographs; 
the difference between these two exposures arise from $Offset$ time, 
that is the time between end and start of a photography.
\begin{table}[h!]
\centering
\begin{tabular}{||c c c c c||} 
 \hline
 $Shutter$ &  $Base$ [$\mu s$] & $Offset$ [$\mu s$] & $E$ [$ms$] & $F_s$ [$fps$]\\ [0.5ex] 
 \hline\hline
 3332  & 20  & 12  & 66.652  & 15.003  \\ 
 1665  & 20  & 12  & 33.312  & 30.019  \\ 
 1110  & 20  & 12  & 22.212  & 45.021  \\ 
 832   & 20  & 12  & 16.652  & 60.053  \\ [1ex] 
 \hline
\end{tabular}
\caption{Exposition time and sampling frequency}
\label{table:1}
\end{table}

\subsection{Data packages in the ink drying process}
\label{subsec:data1}
 This data package analyze a drying ink process, 
 where images data packages are taken at the times
 $\{0,$ $1,$ $2,$ $3,$ $4,$ $5,$ $6,$ $7,$ $8,$ $9,$ $10\}$ min. 
 In each time, the package
 has 512 images of 147 pixels of height and 166 pixels of width.
 They were use 4 different sampling frequencies to the images in each package,
 being these frequencies $15$, $30$, $45$ and $60$ hz.

\subsection{Data package of the activity analysis in corn seed}
\label{subsec:data2}
 This data package analyze the activity of a corn seed with 3 days of germination. 
 In this point, 
 They are taken 4 image data packages with different sampling frequencies to each package,
 being these frequencies $15$, $30$, $45$ and $60$ hz.
 Each package has 512 images of $15$ pixels of height and $15$ pixels of width.

\subsection{Test 1: ink drying process}
\label{subsec:test1}
The Fig. \ref{fig:test1} represents the data analysis method, acquired at a 
sampling frequency of $F_s$, 
with the characteristic seen in the Section \ref{subsec:data1},
\begin{figure}[ht!]
\centering
\includegraphics[width=0.55\columnwidth]{test1.eps}
\caption{Data analysis of the ink drying process test.}
\label{fig:test1}
\end{figure}
where, $P(t)$ is an image data package at the time $t$ minutes, 
being that this package has $N$ images and $M$ pixels, where $P_{n,m}(t)$ 
define the $n$-th image and $m$-th pixel, for all $1 \leq n \leq N$, $1 \leq m \leq M$.
The $MEAN$ block represents the calculus of a temporal speckle mean index from 
the package $P(t)$, returning the value $MEAN(t)$, as exposed in the Section \ref{sec:mean}. 
The $AVD$ block represents the calculus of an absolute values of the differences index from 
the package $P(t)$, returning the value $AVD(t)$, as exposed in the Section \ref{sec:avd}. 
The $STD$ block represents the calculus of a temporal speckle standard deviation index from 
the package $P(t)$, returning the value $STD(t)$, as exposed in the Section \ref{sec:std}.
And finally,
the block $HPF$ represents a digital finite impulse response ``high-pass filter'' 
with order $40$ and cut-off at $0.25F_s$ and this block filter the $P(t)$ package and return $Q(t)$,
that causes to have at end of path the $STDF(t)$ index value.
According the information of the data packages, 
we will have speckle indexes values, for each minute during 10 minutes.

\subsection{Test 2: Activity analysis in corn seed}
\label{subsec:test2}
The activity analysis of a corn seed, 
uses the information of data package seen in the Section \ref{subsec:data2}.
We analyze this information of similar way to the seen in the Section \ref{subsec:test1},
with the difference that is taken an data package at the time $t$ (3 days of germination)
and a sampling frequency $F_s$.

@@

The Fig. \ref{fig:test3} represents the frequency band analysis method of data package $P$, 
acquired  with a sampling frequency of $F_s$. This package pass through the $BPF$ block
described in the Sec \ref{sec:stdb}, with a frequency band pass between $f_1(l)$ and $f_2(l)$,
according the Eq. \ref{eq:f1f2}, where $l$ represent the band so that $1\leq l\leq L$,
being $L$ the quantity of analysis frequency bands; 
thus, we obtaining the  $R$ package (a filtered version of $P$). Later, It is processed 
a $\sigma$ block, where It is calculate the $\sigma_{m}$ value to each pixel in the package $R$,
as described in the Sec \ref{sec:std}. Finally, 
an image is obtained and It is designed with the variable $STDB$.
\begin{figure}[ht!]
\centering
\includegraphics[width=0.55\columnwidth]{test3.eps}
\caption{Frequency band analysis of a data package.}
\label{fig:test3}
\end{figure}

@@

In the next subsections we use the variable $P$ to define $P(t)$ in any time $t$.

@@

The temporal speckle mean index ($\mu_{m}$) \cite{Nothdurft:05} calculates the mean
value of the illumination level to the $m$-th pixel in the package $P$, It is implemented
with the Eq. \ref{eq:mu},
\begin{equation}\label{eq:mu}
\mu_{m} = \sum \limits_{n=1}^{N} \frac{P_{n,m}}{N}.
\end{equation}
Finally, the $MEAN$ index is the mean value of all $\mu_{m}$ results,
as can be viewed in the Eq. \ref{eq:MEAN},
\begin{equation}\label{eq:MEAN}
MEAN = \sum \limits_{m=1}^{M} \frac{\mu_{m}}{M}.
\end{equation}

@@

The Absolute Values of the Differences ($AVD_{m}$) \cite{cardoso2014,rivera2017selection} calculates the mean
value of the absolute differences in the illumination level of the $m$-th pixel in the package $P$, It is implemented
with the Eq. \ref{eq:avd0},
\begin{equation}\label{eq:avd0}
AVD_{m} = \sum \limits_{n=2}^{N} \frac{|P_{n,m}-P_{n-1,m}|}{N}.
\end{equation}
Finally, the $AVD$ index is the mean value of all $AVD_{m}$ results,
as can be viewed in the Eq. \ref{eq:AVD},
\begin{equation}\label{eq:AVD}
AVD = \sum \limits_{m=1}^{M} \frac{AVD_{m}}{M}
\end{equation}

@@

The temporal speckle standard deviation index ($\sigma_{m}$) \cite{Nothdurft:05} calculates the standard deviation
value of the illumination level to the $m$-th pixel in the package $P$, It is implemented
with the Eq. \ref{eq:sigma},
\begin{equation}\label{eq:sigma}
\sigma_{m}^2 = \sum \limits_{n=1}^{N} \frac{(P_{n,m}-\mu_{m})^2}{N}.
\end{equation}
Finally, the $STD$ index is the mean value of all $\sigma_{m}$ results,
as can be viewed in the Eq. \ref{eq:STD},
\begin{equation}\label{eq:STD}
STD = \sum \limits_{m=1}^{M} \frac{\sigma_{m}}{M}
\end{equation}

@@

The high-pass filter ($HPF$) block It is implemented with a finite impulse 
response ($FIR$)\cite{saramaki1993finite} filter
of order 40 and cut-off at $0.25F_s$. 
The 41 values in the filter are represented with $h(i)$, for all $0 \leq i\leq 40$ and zero in others cases, so that
if we send a data package $P$ through the $HPF$ block we obtain a data package $Q$,
as can be seen in the Eq. \ref{eq:fir},
\begin{equation}\label{eq:fir}
Q_{n,m} = \sum_{k=1}^{N} P_{k,m} h(n-k+20}).
\end{equation}

@@

The band-pass filter ($BPF$) block, 
It is implemented similarly as the see in Sec. \ref{sec:stdf}, 
 with  a $FIR$ filter of order 40 but with a cut-off in $f_1(l)$ and $f_2(l)$, 
\begin{equation}\label{eq:f1f2}
\left [ f_1(l),~f_2(l)\right ] = \left [\frac{(l-1)}{L},~\frac{l}{L} \right ]\frac{F_s}{2},
\end{equation}
representing $l$, for all $1 \leq l \leq L$, the $l$-th band of $L$ parts; so that each band has $\frac{F_s}{2L}$ Hz.
The filter is represented with $g(i)$, for all $0 \leq i\leq 40$ and zero in others cases, so that
if we send a data package $P$ through the $BPF$ block we obtain a data package $R$,
as can be seen in the Eq. \ref{eq:firb},
\begin{equation}\label{eq:firb}
R_{n,m} = \sum_{k=1}^{N} P_{k,m}~g(n-k+20}).
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Result of test 1}
\label{subsec:resulttest1}
This test shows the analyze result of an ink drying process, across 10 minutes,
with the sampling frequency: $15$, $30$, $45$ and $60$Hz.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Figure \ref{fig:MEANtest1} analyze the $MEAN(t)$ index,
in the test showed in the Section \ref{subsec:test1},
to each time $t$ for 4 sampling frequencies.
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{FPS_f11_rawMEAN.eps}
    \caption{$MEAN$ index value.}\label{fig:MEANtest1}
\end{figure}
It easy to see as the value of index has a monotonous 
behavior over time. By other side the values in the curves decreases in proportion with 
the grow of sampling frequency.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Figure \ref{fig:AVDtest1} shows the result of analysis explained in the 
Section \ref{subsec:test1} about the $AVD(t)$ index.
\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \caption{$AVD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_rawAVD.eps}
        \label{fig:avdraw}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}{0.48\textwidth}
        \caption{Normalized $AVD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_norm1AVD.eps}
        \label{fig:avdnorm}
    \end{subfigure}
    \caption{$AVD$ index anaysis.}\label{fig:AVDtest1}
\end{figure}
The Figure \ref{fig:avdraw} shows the $AVD(t)$ index, in each time $t$, 
to 4 sampling frequencies, showing a different behavior across time in each sampling frequency,
so that, the value of the index in all  the curve decreases in proportion with 
the grow of sampling frequency. By other side,
the Figure \ref{fig:avdnorm} shows a normalized version of $AVD(t)$ index, 
so that the maximum value of curves have an unit value; thus,
It is easy to see that the maximum excursion of the curve is greater when decrease
the sampling frequency. Remembering that this index use information in a frequency
band between $F_s/4$ until $F_s/2$ Hz, as seen in Section \ref{sec:avd}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Figure \ref{fig:STDtest1} analyze the $STD(t)$ index in the test showed in the 
Section \ref{subsec:test1}.
\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \caption{$STD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_rawSTD.eps}
        \label{fig:stdraw}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}{0.48\textwidth}
        \caption{Normalized $STD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_norm1STD.eps}
        \label{fig:stdnorm}
    \end{subfigure}
    \caption{$STD$ index anaysis.}\label{fig:STDtest1}
\end{figure}
The Figure \ref{fig:stdraw} shows the  behavior of $STD(t)$ index, in each time $t$, 
to 4 different sampling frequencies. Remembering that this index uses information in a frequency
band between $0$ until $F_s/2$ Hz, as seen in Section \ref{sec:std}.
This index shows a different behavior across time to each sampling frequency,
so that, the value of the index in each time of curve decreases in proportion with 
the grow of sampling frequency. By other side,
the Figure \ref{fig:stdnorm} shows a normalized version of $STD(t)$ index;
being the unit, the maximum value of curves; thus,
It is easy to see that exist a small difference between the maximum excursion 
of the curves with different sampling frequency; even so, It is possible to observe
a decrease of the maximum excursion in the curve with the grow of the sampling frequency.

>>>>

\title{Sampling Frequency in the Dynamic Speckle Analysis}
%\tnotetext[mytitlenote]{Fully documented templates are available in the 
%elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

% Group authors per affiliation:
\author{Rivera, F. P.}
\author{Pe\~na, R. G.}
\author{Braga, R. A.}

\address{University Federal of Lavras, Lavras, Brazil}
%\fntext[myfootnote2]{201518201@posgrad.ufla.br}
%\fntext[myfootnote1]{robertobraga@deg.ufla.br }
%

\begin{abstract}
In this article, we show as the variation of sampling frequency, 
in a dynamic speckle analysis, affects the value of some dynamic speckle index, 
to the cases of the absolute value of the differences index, the temporal 
speckle standard deviation index and the temporal 
speckle mean index.
We show that  the dynamic speckle index value change the maximum excursion with 
the variation of sampling frequency, affected directly by the time integration 
(exposition time) of camera.
We highlight the importance of knowing  the frequency band of analyzed phenomenon, 
in order to choose the appropriate sampling frequency, 
being recommendable to use the minimal sampling frequency possible
to get an acceptable maximum excursion, 
and an illumination level with good signal-noise ratio.

\end{abstract}

\begin{keyword}
Sampling frequency \sep
Dynamic speckle index \sep 
Dynamic speckle index \sep 
Dynamic speckle analysis
\end{keyword}

@@

%1) Anuncie o tema e o problema do artigo (forma de pergunta + definiçoes)
The dynamic laser speckle analysis is  an important
study topic\cite{catalano2019viability,rivera2019sound,gonzalez2018diode,Silva2018,braga2017dynamic} 
to determine the  activity level of biological materials. 
The importance of technical aspects of dynamic laser speckle analysis,
as the stability of laser illumination level has been  analyzed \cite{gonzalez2018diode}, 
and it was analyzed the effect of illumination instability over an index value \cite{gonzalez2018diode},
such as the absolute values of the differences \cite{cardoso2014,rivera2017selection}.
It  was showed the dependence between the index value and the illumination level.

%3) Resgate a problematica( Importancia do problema de pesquisa - extenda primer passo)
Thus, 
it is necessary analyze the effect of technical parameters that affect the perceived illumination level; 
in these sense,
we analyze the effect of sampling frequency, 
and consequently the time exposure, in a dynamic laser speckle analysis
that use: the absolute value of the differences index, 
the temporal speckle standard deviation index and the temporal speckle mean index \cite{Nothdurft:05}.

%4) Relevancia do artigo(importancia para outros del artigo publicado)
Knowing the effect of sampling frequency over an index value,
a researcher will be able to have a criteria to choose the appropriate sampling frequency 
for a certain monitored phenomenon. 
% Thus,
% optimizing resources when choosing the hardware specification in a system setup; 
% being in this case, the limitations relatives to illumination level and signal-noise relation in the study sample.

%5) Anuncie a hipotesis
For this purpose, we show that given a dynamic speckle test, exists an appropriate frequency band
to the sampling frequency. High values of sampling rate may cause unintended consequences on the index value, 
such as the decrease of the excursion between two activity levels, given a determinate index value. 
In turn, decreasing the sampling frequency promoted by the increasing of the exposure time,
will cause a reduction of the temporal speckle contrast,
 and consequently limit the possibility  to get information from the sample.

%6) Anuncie os objetivos (receita pra demostrar a h.)
To be able to demonstrate the existence of this appropriate frequency band,
we will perform two types of tests; in the first, we analyzed an ink drying process along the time; and in
the second, we tested the activity state of a corn seed, with 3 days of germination.
In both cases, were used four different sampling rates, 
and was compared the behavior of speckle indexes.

%2) Exponha qual será o percurso (defina seçoes)
In the next section we describe how the speckle images were acquired and the setup used to analyze them; 
all theoretical definitions, necessary to understand the analysis, will shown in the Section 3;
numerical results of the analysis  are presented in Section 4, and
an analysis of the results is reported in the Section 5; finally, we present our
conclusion in the Section 6.

@@

\subsection{Time exposure of the camera}
\label{subsec:expositiontime}
The sampling frequency ($F_s$) or acquisition time in frames per second ($fps$), 
in the camera Marlin F-033 is obtained using the 
 Table \ref{table:1}, 
\begin{table}[h!]
\centering
\begin{tabular}{||c c c c c||} 
 \hline
 $Shutter$ &  $Base$ [$\mu s$] & $Offset$ [$\mu s$] & $E$ [$ms$] & $F_s$ [$fps$]\\ [0.5ex] 
 \hline\hline
 3332  & 20  & 12  & 66.652  & 15.003  \\ 
 1665  & 20  & 12  & 33.312  & 30.019  \\ 
 1110  & 20  & 12  & 22.212  & 45.021  \\ 
 832   & 20  & 12  & 16.652  & 60.053  \\ [1ex] 
 \hline
\end{tabular}
\caption{Exposition time and sampling frequency}
\label{table:1}
\end{table}
where we can see the 4 sampling frequencies that will be used in the tests;
these values were obtained using  
the shutter register value ($Shutter$), 
the time base register value ($Base$),
the exposure time offset ($Offset$) and
the effective exposure time ($E$);
 so that the exposure time ($Exposure$),
\begin{equation}
Exposure= Shutter \times Base,
\end{equation}
\begin{equation}
\frac{1}{F_s}=E= Exposure + Offset.
\end{equation}
Where,  $F_s$ is calculated in relation to $E$; being that,
the $Exposure$ represent the photography integration time and $E$ the effective time
between photographs; 
the difference between these two exposures arise from $Offset$ time, 
that is the time between end and start of a photography.
In all cases the exposure time is much bigger than $Offset$; so, we can approximate
that $F_s\approx 1/Exposure$.

\subsection{Data-packages of ink drying process}
\label{subsec:data1}
 This data set comes from an ink drying process, 
 where groups of images (data package) are taken at the times
 $\{0,$ $1,$ $2,$ $3,$ $4,$ $5,$ $6,$ $7,$ $8,$ $9,$ $10\}$ min. 
 In each time, an acquired package  has 512 images of 147 pixels of height and 166 pixels of width.
4 different sampling rates were used to take the images,
 being these rates $15$, $30$, $45$ and $60$ hz.

\subsection{Data-package of maize seed germination}
\label{subsec:data2}
 This data-package has the speckle pattern of a maize seed with 3 days of germination,
 where four data-packages with different sampling rates ( $15$, $30$, $45$ and $60$ hz)  
were built.
Each package have 512 images of $15$ pixels of height and $15$ pixels of width.

\subsection{Test 1: ink drying process}
\label{subsec:test1}
Fig. \ref{fig:test1} represents the data analysis method in an ink drying process, 
to a $F_s$ sampling rate.
\begin{figure}[ht!]
\centering
\includegraphics[width=0.55\columnwidth]{test1.eps}
\caption{Data analysis of the ink drying process test.}
\label{fig:test1}
\end{figure}
Where, $P(t)$ is an data-package with  images at the time $t$ minutes; 
this package has $N$ images and $M$ pixels; $P_{n,m}(t)$ 
define the $n$-th image and $m$-th pixel, for all $1 \leq n \leq N$, $1 \leq m \leq M$.
The $MEAN$ block represents the calculation of temporal speckle mean index on 
the package $P(t)$, returning the value $MEAN(t)$. 
The $AVD$ block represents the calculation of  absolute values of the differences index on
the package $P(t)$, returning the value $AVD(t)$. 
The $STD$ block represents the calculation of the temporal speckle standard deviation index on 
the package $P(t)$ or $Q(t)$, returning the value $STD(t)$ or $STDF(t)$, respectively.
And finally,
the block \hyperref[sec:stdf]{$HPF$} represents a digital finite impulse response ``high-pass filter'' 
with order $40$ and cut-off at $0.25F_s$; this block filter the $P(t)$ package and return $Q(t)$,
leading this result to a $STD$ block to finally obtain the $STDF(t)$ index value.
According to the information of the data packages, 
we will have speckle indexes values, for each minute, during 10 minutes.

\subsection{Test 2: Maize seed germination}
\label{subsec:test2}
The speckle activity of a maize seed
was analyzed in a similar way to the ink drying, seen in the Section \ref{subsec:test1}, 
with the difference that only one data-package was taken at the time $t$, equal to 3 days of germination.

@@

The Fig. \ref{fig:test3} represents the frequency band analysis method of data package $P$, 
acquired  with a sampling rate of $F_s$. This package is the input of many band pass filter (\hyperref[sec:stdb]{$BPF$}) blocks,
described in the Sec \ref{sec:stdb}, these band pass filter have cut-off frequencies between $f_1(l)$ and $f_2(l)$,
where $l$ indicates the current band, so that $1\leq l\leq L$;
being $L$ the total number of analysis frequency bands; 
thus, we obtained the  $R_l$ package (a filtered version of $P$). $R_l$ was processed 
by a $\sigma$ block, where it is calculated the $\sigma_{m}$ value to each pixel in the package $R_l$,
as described in the Sec \ref{sec:std}. Finally, 
an image is obtained and it is named as the variable $STDB_l$.
\begin{figure}[ht!]
\centering
\includegraphics[width=0.55\columnwidth]{test3.eps}
\caption{Frequency band analysis of a data package.}
\label{fig:test3}
\end{figure}

@@

In the next subsections we use the variable $P$ to define $P(t)$ in any time $t$;
thus, $P$ represents a data collection of images in any time.

@@

The temporal speckle mean index ($\mu_{m}$) \cite{Nothdurft:05} gives the mean
value of the illumination level to the $m$-th pixel in the package $P$, 
and it was  implemented as presented in Eq. \ref{eq:mu}, where $N$ is the number of image in the package,
\begin{equation}\label{eq:mu}
\mu_{m} = \sum \limits_{n=1}^{N} \frac{P_{n,m}}{N}.
\end{equation}
Finally, the $MEAN(t)$ index is the spatial mean value of all $\mu_{m}$ results,
as can be viewed in the Eq. \ref{eq:MEAN},
\begin{equation}\label{eq:MEAN}
MEAN(t) = \sum \limits_{m=1}^{M} \frac{\mu_{m}}{M}.
\end{equation}

@@

The Absolute Values of the Differences ($AVD_{m}$) \cite{cardoso2014,rivera2017selection} gives the mean
value of the absolute differences in the illumination level of the $m$-th pixel in the package $P$, it was  implemented
by Eq. \ref{eq:avd0},
\begin{equation}\label{eq:avd0}
AVD_{m} = \sum \limits_{n=2}^{N} \frac{|P_{n,m}-P_{n-1,m}|}{N}.
\end{equation}
Finally, the $AVD(t)$ index is the spatial mean value of all $AVD_{m}$ results,
as can be viewed in the Eq. \ref{eq:AVD},
\begin{equation}\label{eq:AVD}
AVD(t) = \sum \limits_{m=1}^{M} \frac{AVD_{m}}{M}
\end{equation}

@@

The temporal speckle standard deviation index ($\sigma_{m}$) \cite{Nothdurft:05} gives the standard deviation
value of the illumination level to the $m$-th pixel in the package $P$, it was implemented
with the Eq. \ref{eq:sigma},
\begin{equation}\label{eq:sigma}
\sigma_{m}^2 = \sum \limits_{n=1}^{N} \frac{(P_{n,m}-\mu_{m})^2}{N}.
\end{equation}
Finally, the $STD(t)$ index is the spatial mean value of all $\sigma_{m}$ results,
as can be viewed in the Eq. \ref{eq:STD},
\begin{equation}\label{eq:STD}
STD(t) = \sum \limits_{m=1}^{M} \frac{\sigma_{m}}{M}
\end{equation}

@@

The high-pass filter ($HPF$) block was implemented (Fig. \ref{fig:test1}) with a finite impulse 
response ($FIR$)\cite{saramaki1993finite} filter
of order 40 and cut-off at $0.25F_s$. 
The 41 values in the filter are represented with $h(i)$, for all $0 \leq i\leq 40$, with zero in others cases.
Thus, a data package $P$ as input of the $HPF$ block gives us as result, a data package $Q$,
as can be seen in the Eq. \ref{eq:fir},
\begin{equation}\label{eq:fir}
Q_{n,m} = \sum_{k=1}^{N} P_{k,m} h(n-k+20}).
\end{equation}

@@

The band-pass filter ($BPF$) block  is implemented (Fig. \ref{fig:test3}) similarly as the \hyperref[sec:stdf]{$HPF$} block, 
 with  a $FIR$ filter of order 40 but with a cut-off in $f_1(l)$ and $f_2(l)$, 
\begin{equation}\label{eq:f1f2}
\left [ f_1(l),~f_2(l)\right ] = \left [\frac{(l-1)}{L},~\frac{l}{L} \right ]\frac{F_s}{2},
\end{equation}
representing $l$, for all $1 \leq l \leq L$, the $l$-th band of $L$ bands; each band has $\frac{F_s}{2L}$ Hz.
The filter is represented with $g(i)$, for all $0 \leq i\leq 40$, with zero in others cases. 
Thus, a data package $P$ as input of the $BPF$ block gives us as result, a data package $R$,
as can be seen in the Eq. \ref{eq:firb},
\begin{equation}\label{eq:firb}
R_{n,m} = \sum_{k=1}^{N} P_{k,m}~g(n-k+20}).
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Test 1: ink drying process}
\label{subsec:resulttest1}
This test shows the analysis result of an ink drying process, during 10 minutes,
using the sampling rates: $15$, $30$, $45$ and $60$Hz.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Figure \ref{fig:MEANtest1} presents the $MEAN(t)$ index,
in the test showed in the Section \ref{subsec:test1},
to each time $t$ for the  4 sampling rates.
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{FPS_f11_rawMEAN.eps}
    \caption{$MEAN$ index value.}\label{fig:MEANtest1}
\end{figure}
It can be seen that, 
the value of index has a monotonous behavior over time. 
By other side the values in the curves decreases in proportion with 
the grow of sampling rate.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Figure \ref{fig:AVDtest1} shows the result of analysis explained in the 
Section \ref{subsec:test1} about the $AVD(t)$ index.
\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \caption{$AVD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_rawAVD.eps}
        \label{fig:avdraw}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}{0.48\textwidth}
        \caption{Normalized $AVD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_norm1AVD.eps}
        \label{fig:avdnorm}
    \end{subfigure}
    \caption{$AVD$ index anaysis.}\label{fig:AVDtest1}
\end{figure}
The Figure \ref{fig:avdraw} shows the $AVD(t)$ index, in each time $t$, 
to 4 sampling rates, showing a different behavior in time to each sampling rate,
so that, the value of the index in all  curves, decreases in proportion with 
the grow of sampling rate. By other side,
Figure \ref{fig:avdnorm} shows a normalized version of $AVD(t)$ index, 
so that the maximum value of curves have an unit value; thus,
it can be seen that, the maximum excursion of the curve is greatest when 
the sampling rate decrease. Remembering that this index uses information from a frequency
band between $F_s/4$ until $F_s/2$ Hz \cite{rivera2017selection}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Figure \ref{fig:STDtest1} presents the $STD(t)$ index in the test showed in the 
Section \ref{subsec:test1}.
\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \caption{$STD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_rawSTD.eps}
        \label{fig:stdraw}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}{0.48\textwidth}
        \caption{Normalized $STD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_norm1STD.eps}
        \label{fig:stdnorm}
    \end{subfigure}
    \caption{$STD$ index anaysis.}\label{fig:STDtest1}
\end{figure}
The Figure \ref{fig:stdraw} shows the  behavior of $STD(t)$ index, in each time $t$, 
to 4 different sampling rates. Remembering that this index uses information in the entire frequency
band ($0$ until $F_s/2$ Hz), as seen in Section \ref{sec:std}.
This index shows a different behavior in time to each sampling frequency,
so that, the value of the index in each time  decreases in proportion with 
the grow of sampling rate. By other side,
Figure \ref{fig:stdnorm} shows a normalized version of $STD(t)$ index;
being the unit, the maximum value of curves; thus,
it can be seen that exists a small difference between the maximum excursion 
of the curves with different sampling rates; even so, it is possible to observe
a slight decrease of the maximum excursion in the curve with the grow of the sampling rate, 
unlike the $AVD(t)$ index.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Figure \ref{fig:STDFtest1}, presents the $STDF(t)$ index, in the test showed in the 
Section \ref{subsec:test1}.
\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \caption{$STDF$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_rawSTDF.eps}
        \label{fig:stdfraw}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}{0.48\textwidth}
        \caption{Normalized $STDF$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_norm1STDF.eps}
        \label{fig:stdfnorm}
    \end{subfigure}
    \caption{$STDF$ index anaysis.}\label{fig:STDFtest1}
\end{figure}
Figure \ref{fig:stdfraw} shows the behavior $STDF(t)$ index, in each time $t$, 
to 4 different sampling rates. Remembering that this index uses filtered 
information of datapack, so that the frequency
band is between $F_s/4$ and $F_s/2$ Hz. 
% of similar way of $AVD(t)$ index but with different order filter, as seen in Section \ref{sec:stdf}.
This index shows monotone decreasing behavior in time, where we observe 
a different behavior in time to each different sampling rate;
so that, the value of the index in each time decreases in proportion with 
the grow of sampling rate. By other side,
Figure \ref{fig:stdfnorm} shows a normalized version of $STDF(t)$ index;
being the unit, the maximum value of curves; thus,
it can be seen that exists a considerable difference between the maximum excursion 
of the curves with the use of sampling frequency; so, it is possible to observe a 
grow of the maximum excursion when the sampling rate decrease, like the $AVD(t)$ index.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Test 2: maize seed germination}
\label{subsec:resulttest2}

This test shows the result of analyze a corn seed  with 3 days of germination,
the images were taken using the sampling rates: $15$, $30$, $45$ and $60$Hz.
